---
title: "Spotify playlist report"
output:
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
library(GGally)
library(wordcloud2) 
library(forcats)
library(data.table)
library(tidyverse)
library(plotly)
library(viridis)
library(hrbrthemes)
library(corrplot)
library(DT)
library(ggthemes)
```

```{r, echo=FALSE}
source("funs.R")
source("playlist_features_poc.R")
```

# Every column in a data frame

```{r, echo=FALSE}
glimpse(playlist_audio_features)
```

# Summary and Descriptive Statistics of songs atributes

```{r, echo=FALSE}
summary(playlist_audio_features_sliced)
```
# How many songs of that type do we have in our playlist

```{r, echo=FALSE}
  name <- playlist_audio_features %>%
  group_by(playlist_name, track.name, track.album.name) %>%
  dplyr::summarize(Total = n()) 
datatable(name)
```


# How the popularities are distribuited
Most songs has a popularity between 62.8 and 78.4

```{r, echo=FALSE}
library(dplyr)
playlist_audio_features$track.popularity <- cut(playlist_audio_features$track.popularity, breaks = 5)
playlist_audio_features %>%
  ggplot( aes(x=track.popularity ))+
  geom_bar(width=0.2) +
  coord_flip() +
  scale_x_discrete(name="Popularity")  + theme_gray() 
```


# How the energy are distribuited
```{r, echo=FALSE}
playlist_audio_features$energy <- cut(playlist_audio_features$energy, breaks = 10)
playlist_audio_features %>%
  ggplot( aes(x=energy ))+
  geom_bar(width=0.2) +
  coord_flip() +
  scale_x_discrete(name="Energy")  + theme_gray() 
```

# How the song's lenght are distribuited
Lets see the most commum lenght

```{r, echo=FALSE}
playlist_audio_features$track.duration_ms <- cut(playlist_audio_features$track.duration_ms, breaks = 10)
playlist_audio_features %>%
  ggplot( aes(x=track.duration_ms ))+
  geom_bar(width=0.2) +
  coord_flip() +
  scale_x_discrete(name="Length")  + theme_gray() 
```


# Correlation between atribiutes of song 

```{r}
options(repr.plot.width = 20, repr.plot.height = 15)
playlist_audio_features_sliced <- playlist_audio_features[, 6:16]
playlist_audio_features_sliced <- playlist_audio_features_sliced[,-2]
corr <- cor(playlist_audio_features_sliced)

num <- corrplot(corr, method = "number")
```

# Histogram for each features

```{r}
playlist_audio_features_sliced %>%
  gather(Features, value, 0:10) %>%
  ggplot(aes(x=value, fill=Features)) +
  geom_histogram(colour="black", show.legend=FALSE) +
  facet_wrap(~Features, scales="free_x") +
  labs(x="Values", y="Frequency",
       title="Song Features - Histograms") +
  theme_bw()
```
```


